Air cargo load and route planning in pickup and delivery operations

### 2024-02-02 latex/eswa.tex
New experiments

\begin{center}
	%\fbox{
		\begin{tikzpicture}
			\begin{axis}[xmin=6,ymin=80,
				enlarge y limits={upper,value=0.2},
				xlabel style={align=center},
				xlabel={Number of nodes},
				ylabel={Time (s)},
				xtick={  5,  6,   7,   8,   9,  10,  11,  12,  13,  14,  15,  16},
				ytick={80,100,120,140,160,180,200,220,240,260,280,300},						
				]
				\addplot[
				blue,
				thick,
				mark=*,
				mark options={fill=blue},
				visualization depends on=\thisrow{alignment} \as \alignment,
				nodes near coords, % Place nodes near each coordinate
				point meta=explicit symbolic, % The meta data used in the nodes is not explicitly provided and not numeric
				every node near coord/.style={anchor=\alignment} % Align each coordinate at the anchor 40 degrees clockwise from the right edge
				] table [% Provide data as a table
				meta index=2 % the meta data is found in the third column
				] {
					x   y    label                 alignment
					7   99  {\footnotesize 91.9}  -10
					8   126  {\footnotesize 108.2} -10
					9   145  {\footnotesize 108.7} -10
					10  168 {\footnotesize 111.2} -10
					11  191 {\footnotesize 78.0}  -10
					12  215 {\footnotesize 84.1}  -10
					13  239 {\footnotesize 93.3}  -10
					14  264 {\footnotesize 104.8} -10									
					15  293 {\footnotesize 96.1}  -10									
				};
			\end{axis}
		\end{tikzpicture}
		%}
	\captionof{figure}{Shims performance (total time)}
\end{center}

>>>>

\begin{center}
	%\fbox{
		\begin{tikzpicture}
			\begin{axis}[xmin=6,ymin=80,
				enlarge y limits={upper,value=0.2},
				xlabel style={align=center},
				xlabel={Number of nodes},
				ylabel={Time (s)},
				xtick={  5,  6,   7,   8,   9,  10,  11,  12,  13,  14,  15,  16},
				ytick={80,100,120,140,160,180,200,220,240,260,280,300},						
				]
				\addplot[
				blue,
				thick,
				mark=*,
				mark options={fill=blue},
				visualization depends on=\thisrow{alignment} \as \alignment,
				nodes near coords, % Place nodes near each coordinate
				point meta=explicit symbolic, % The meta data used in the nodes is not explicitly provided and not numeric
				every node near coord/.style={anchor=\alignment} % Align each coordinate at the anchor 40 degrees clockwise from the right edge
				] table [% Provide data as a table
				meta index=2 % the meta data is found in the third column
				] {
					x   y    label                 alignment
					7   99  {\footnotesize 91.9}  -10
					8   126  {\footnotesize 108.2} -10
					9   145  {\footnotesize 108.7} -10
					10  168 {\footnotesize 111.2} -10
					11  191 {\footnotesize 78.0}  -10
					12  215 {\footnotesize 84.1}  -10
					13  239 {\footnotesize 93.3}  -10
					14  264 {\footnotesize 104.8} -10									
					15  293 {\footnotesize 96.1}  -10									
				};
			\end{axis}
		\end{tikzpicture}
		%}
	\captionof{figure}{Shims performance (new time computation)}
\end{center}

	\begin{center}
		%\fbox{
			\begin{tikzpicture}
				\begin{axis}[xmin=6,ymin=600,
					enlarge y limits={upper,value=0.2},
					xlabel style={align=center},
					xlabel={Number of nodes},
					ylabel={Time (s)},
					xtick={  5,  6,   7,   8,   9,  10,  11,  12,  13,  14,  15,  16},
					ytick={600,1850,3100,4350,5600,6850,8100,9350,10600,11850,13100,14350},						
					]
					\addplot[
					blue,
					thick,
					mark=*,
					mark options={fill=blue},
					visualization depends on=\thisrow{alignment} \as \alignment,
					nodes near coords, % Place nodes near each coordinate
					point meta=explicit symbolic, % The meta data used in the nodes is not explicitly provided and not numeric
					every node near coord/.style={anchor=\alignment} % Align each coordinate at the anchor 40 degrees clockwise from the right edge
					] table [% Provide data as a table
					meta index=2 % the meta data is found in the third column
					] {
						x   y    label                 alignment
						7   692  {\footnotesize 91.9}  -10
						8   1570  {\footnotesize 108.2} -10
						9   2580  {\footnotesize 108.7} -10
						10  3754 {\footnotesize 111.2} -10
						11  5086 {\footnotesize 78.0}  -10
						12  6589 {\footnotesize 84.1}  -10
						13  8528 {\footnotesize 93.3}  -10
						14  10101 {\footnotesize 104.8} -10									
						15  12150 {\footnotesize 96.1}  -10									
					};
				\end{axis}
			\end{tikzpicture}
			%}
		\captionof{figure}{Shims performance (total time)}
	\end{center}
